\systemnamenospace: Head Orientation-Based Selection\\in Physical Spaces

### 2014-08-14 doc/sui14/relatedwork.tex
Minor, remove trailing spaces
added related work of Hipp'09, also tried to use 80-column rules for the texts
added low cost solution argument to hipp
removed useless whitespace

\subsection{Pointing in Physical Spaces}
Rukzio ~\cite{rukzio_experimental_2006} studied alternative methods for selecting devices in physical spaces and found that users strongly preferred either tapping target appliances with a mobile device or pointing at a distance to browsing a list. Several other approaches to spatial selection with handheld devices~\cite{beigl_point_1999,patel_2-way_2003,wilson_xwand:_2003,schmidt_picontrol:_2012,kemp_point-and-click_2008} or finger-worn devices~\cite{merrill_augmenting_2007} exist. 
%and exchanging information with smart infrastructure sensor networks ~\cite{lifton_tricorder:_2007,mittal_ubicorder:_2011,costanza_sensortune:_2010}. 
In some techniques, users select objects of interest with laser pointers; however, the laser dot's small target area makes it poorly matched to head orientation input.
Other approaches rely on virtual room models in which a user's location is estimated using IMU-based orientation sensing~\cite{wilson_xwand:_2003,lifton_tricorder:_2007} -- in contrast, our technique does not require a static map ahead of time.
%Other targeting systems use IR with handheld pointers~\cite{swindells_that_2002} as well as wearable devices such as rings and Bluetooth audio earpieces~\cite{merrill_augmenting_2007} to connect to smart devices. 
Our system tackles an unresolved issue of prior approaches -- navigating an area dense with potential targets and resolving selection ambiguity.

>>>>

\subsection{Pointing in Physical Spaces}
Rukzio \changes{et al.}~\cite{rukzio_experimental_2006} studied alternative
methods for selecting devices in physical spaces and found that users strongly
preferred either tapping target appliances with a mobile device or pointing at a
distance to browsing a list. Several other approaches to spatial selection with
handheld
devices~\cite{beigl_point_1999,patel_2-way_2003,wilson_xwand:_2003,schmidt_picontrol:_2012,kemp_point-and-click_2008}
or finger-worn devices~\cite{merrill_augmenting_2007} exist.
%and exchanging information with smart infrastructure sensor networks ~\cite{lifton_tricorder:_2007,mittal_ubicorder:_2011,costanza_sensortune:_2010}.

In some techniques, users select objects of interest with laser pointers;
however, the laser dot's small target area makes it poorly matched to head
orientation input.  Other approaches rely on virtual room models in which a
user's location is estimated using IMU-based orientation
sensing~\cite{wilson_xwand:_2003,lifton_tricorder:_2007} -- in contrast, our
technique does not require a static map ahead of time. \changes{In the FreeMote
system, \cite{hipp2009universal} an IR camera in a handheld controller interprets readings from IR emitters on target appliances. In contrast, we explore a lower cost alternative, using only IR emitters and receivers. }
% Other targeting systems use IR with handheld
% pointers~\cite{swindells_that_2002} as well as wearable devices such as rings
% and Bluetooth audio earpieces~\cite{merrill_augmenting_2007} to connect to
% smart devices.
Our system tackles an unresolved issue of prior approaches -- navigating an area
dense with potential targets and resolving selection ambiguity.
